---
title: "onfant.dataset: Late-season corn stalk nitrate test data from field surveys across the Midwest from 2006 to 2018."
author: "Anabelle Laurent and Fernando Miguez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{onfant: Read and Clean Files to Run ONFANT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(onfant.dataset)
```


# Introduction

The **onfant.dataset** is distributed as part of a peer-reviewed article that describes a dataset about late-season corn stalk nitrate measurements across the US Midwest from 2006 to 2018. Two datasets are included:  
- stalk_nitrate_CSNT_dataset that contains the corn stalk nitrate measurements and other variables.  See ?stalk_nitrate_CSNT_dataset for more information.  
- weather_onfant that contains weather information for each field included in stalk_nitrate_CSNT_dataset. See ?weather_onfant for more information.  


## Example

We start by looking at the dataset. 

```{r example}
data("stalk_nitrate_CSNT_dataset")
str(stalk_nitrate_CSNT_dataset)
head(stalk_nitrate_CSNT_dataset)

data("weather_onfant")
head(weather_onfant)
```


## Export the dataset in csv format

```{r export-csv}
write.csv(stalk_nitrate_CSNT_dataset,"Here include the path to export the DataFrame/FileName.csv", row.names = FALSE)

```


## Export the dataset in excel format

```{r export-excel}
install.packages("writexl")
library(writexl)
write_xlsx(clean_merge,"Path to export the DataFrame/FileName.xlsx")

```

